\newcommand{\innovativefeature}{
\section{Innovative Feature}
\label{sec:innovative_feature}

    An innovative feature of this product is a Chatbot feature. General users can ask simple questions like "How is the air quality today?" or "Why is there an alert in my area?" and the chatbot will provide a response based on the data collected by the system. This feature will make it easier for users to quickly access information about environmental conditions without having to navigate through the app or website. On the operators side, the chatbot will be able to provide information about what alerts triggered in a day, recent sensor data, etc. that can be used to quickly assess the current state of the environment and make informed decisions about how to respond to any potential issues. \\

    Other Ideas:
    \begin{itemize}
        \item Color-coded environmental risk map that displays color-coded regions (green, yellow, red) based on current environmental conditions.
        \item Graphs showing historical trends of environmental conditions over time in specific areas
        \item Model to predict future environmental events based on current data and historical trends.
        \item A "Health Score" system that will aggregate data from various sensors (air quality, temperature, noise, etc.) to provide an overall health score for a specific area on a particular day.
        \item Public feedback where users can report environmental issues in their area (e.g., pollution, noise, etc.) and this can be paired with sensor data to provide a more comprehensive view of environmental conditions with a human context.


    \end{itemize}
}